Enhancement of SDR in Thessaloniki

### 2024-09-04 GHI_enh_read_aod_brewer.tex
Commit 2024-09-04 14:14

\title{Enhancement of SDR in Thessaloniki}
\author{Natsis Athanasios\footnote{Laboratory of Atmospheric Physics, AUTH, \href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics, AUTH}}
\date{2024-09-03}

@@

@@

\begin{longtable}[]{@{}
  >{\centering\arraybackslash}p{(\columnwidth - 2\tabcolsep) * \real{0.1806}}
  >{\centering\arraybackslash}p{(\columnwidth - 2\tabcolsep) * \real{0.1806}}@{}}
\caption{AOD change \%/y}\tabularnewline
\toprule\noalign{}
\begin{minipage}[b]{\linewidth}\centering
slope\_pCpY
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
AOD
\end{minipage} \\
\midrule\noalign{}
\endfirsthead
\toprule\noalign{}
\begin{minipage}[b]{\linewidth}\centering
slope\_pCpY
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
AOD
\end{minipage} \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
0.07593 & AOD\_292 \\
0.1666 & AOD\_292.5 \\
0.09945 & AOD\_293 \\
0.09468 & AOD\_293.5 \\
0.05937 & AOD\_294 \\
0.06021 & AOD\_294.5 \\
0.07722 & AOD\_295 \\
0.08395 & AOD\_295.5 \\
0.09015 & AOD\_296 \\
0.0975 & AOD\_296.5 \\
0.09944 & AOD\_297 \\
0.08816 & AOD\_297.5 \\
0.09295 & AOD\_298 \\
0.09489 & AOD\_298.5 \\
0.09257 & AOD\_299 \\
0.09279 & AOD\_299.5 \\
0.09115 & AOD\_300 \\
0.09293 & AOD\_300.5 \\
0.09517 & AOD\_301 \\
0.1004 & AOD\_301.5 \\
0.1001 & AOD\_302 \\
0.09831 & AOD\_302.5 \\
0.1008 & AOD\_303 \\
0.1019 & AOD\_303.5 \\
0.1023 & AOD\_304 \\
0.1034 & AOD\_304.5 \\
0.102 & AOD\_305 \\
0.1014 & AOD\_305.5 \\
0.1026 & AOD\_306 \\
0.09934 & AOD\_306.5 \\
0.09853 & AOD\_307 \\
0.1004 & AOD\_307.5 \\
0.1002 & AOD\_308 \\
0.1001 & AOD\_308.5 \\
0.1017 & AOD\_309 \\
0.1028 & AOD\_309.5 \\
0.1056 & AOD\_310 \\
0.1059 & AOD\_310.5 \\
0.1063 & AOD\_311 \\
0.1058 & AOD\_311.5 \\
0.1036 & AOD\_312 \\
0.1066 & AOD\_312.5 \\
0.1056 & AOD\_313 \\
0.1056 & AOD\_313.5 \\
0.1067 & AOD\_314 \\
0.1065 & AOD\_314.5 \\
0.1072 & AOD\_315 \\
0.108 & AOD\_315.5 \\
0.1068 & AOD\_316 \\
0.1073 & AOD\_316.5 \\
0.1079 & AOD\_317 \\
0.108 & AOD\_317.5 \\
0.1068 & AOD\_318 \\
0.1052 & AOD\_318.5 \\
0.1059 & AOD\_319 \\
0.1054 & AOD\_319.5 \\
0.106 & AOD\_320 \\
0.1062 & AOD\_320.5 \\
0.1071 & AOD\_321 \\
0.1034 & AOD\_321.5 \\
0.1031 & AOD\_322 \\
0.1036 & AOD\_322.5 \\
0.104 & AOD\_323 \\
0.1036 & AOD\_323.5 \\
0.1044 & AOD\_324 \\
0.104 & AOD\_324.5 \\
0.1036 & AOD\_325 \\
0.1024 & AOD\_325.5 \\
0.1032 & AOD\_326 \\
0.1016 & AOD\_326.5 \\
0.1008 & AOD\_327 \\
0.1025 & AOD\_327.5 \\
0.1036 & AOD\_328 \\
0.1041 & AOD\_328.5 \\
0.1047 & AOD\_329 \\
0.1042 & AOD\_329.5 \\
0.1059 & AOD\_330 \\
0.1055 & AOD\_330.5 \\
0.1041 & AOD\_331 \\
0.1045 & AOD\_331.5 \\
0.1038 & AOD\_332 \\
0.1074 & AOD\_332.5 \\
0.1079 & AOD\_333 \\
0.1083 & AOD\_333.5 \\
0.1089 & AOD\_334 \\
0.1102 & AOD\_334.5 \\
0.1103 & AOD\_335 \\
0.1098 & AOD\_335.5 \\
0.11 & AOD\_336 \\
0.1103 & AOD\_336.5 \\
0.11 & AOD\_337 \\
0.1108 & AOD\_337.5 \\
0.1092 & AOD\_338 \\
0.1103 & AOD\_338.5 \\
0.1097 & AOD\_339 \\
0.109 & AOD\_339.5 \\
0.1087 & AOD\_340 \\
0.1091 & AOD\_340.5 \\
0.1094 & AOD\_341 \\
0.1097 & AOD\_341.5 \\
0.1098 & AOD\_342 \\
0.1114 & AOD\_342.5 \\
0.1088 & AOD\_343 \\
0.1086 & AOD\_343.5 \\
0.1088 & AOD\_344 \\
0.1082 & AOD\_344.5 \\
0.1083 & AOD\_345 \\
0.1104 & AOD\_345.5 \\
0.1104 & AOD\_346 \\
0.1103 & AOD\_346.5 \\
0.1091 & AOD\_347 \\
0.109 & AOD\_347.5 \\
0.1085 & AOD\_348 \\
0.1082 & AOD\_348.5 \\
0.1093 & AOD\_349 \\
0.1079 & AOD\_349.5 \\
0.1062 & AOD\_350 \\
0.1042 & AOD\_350.5 \\
0.1049 & AOD\_351 \\
0.104 & AOD\_351.5 \\
0.1034 & AOD\_352 \\
0.1042 & AOD\_352.5 \\
0.1075 & AOD\_353 \\
0.1079 & AOD\_353.5 \\
0.1085 & AOD\_354 \\
0.1135 & AOD\_354.5 \\
0.1145 & AOD\_355 \\
0.1137 & AOD\_355.5 \\
0.1135 & AOD\_356 \\
0.1151 & AOD\_356.5 \\
0.1154 & AOD\_357 \\
0.1148 & AOD\_357.5 \\
0.1163 & AOD\_358 \\
0.1174 & AOD\_358.5 \\
0.1179 & AOD\_359 \\
0.1181 & AOD\_359.5 \\
0.1197 & AOD\_360 \\
0.1188 & AOD\_360.5 \\
0.1179 & AOD\_361 \\
0.1155 & AOD\_361.5 \\
0.1236 & AOD\_362 \\
0.1082 & AOD\_362.5 \\
0.08471 & AOD\_363 \\
\end{longtable}

\begin{verbatim}
range 0.0593665 0.1665588 
\end{verbatim}

@@

>>>>

\title{Enhancement of SDR in Thessaloniki}
\author{Natsis Athanasios\footnote{Laboratory of Atmospheric Physics, AUTH, \href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics, AUTH}}
\date{2024-09-04}

@@

\begin{verbatim}
Limit max AOD to  0.8 
\end{verbatim}

@@

\begin{longtable}[]{@{}
  >{\centering\arraybackslash}p{(\columnwidth - 2\tabcolsep) * \real{0.1806}}
  >{\centering\arraybackslash}p{(\columnwidth - 2\tabcolsep) * \real{0.1806}}@{}}
\caption{AOD change \%/y}\tabularnewline
\toprule\noalign{}
\begin{minipage}[b]{\linewidth}\centering
slope\_pCpY
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
AOD
\end{minipage} \\
\midrule\noalign{}
\endfirsthead
\toprule\noalign{}
\begin{minipage}[b]{\linewidth}\centering
slope\_pCpY
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
AOD
\end{minipage} \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
0.07593 & AOD\_292 \\
0.07434 & AOD\_292.5 \\
0.06485 & AOD\_293 \\
0.03045 & AOD\_293.5 \\
0.003635 & AOD\_294 \\
0.003565 & AOD\_294.5 \\
0.01818 & AOD\_295 \\
0.02132 & AOD\_295.5 \\
0.03856 & AOD\_296 \\
0.05433 & AOD\_296.5 \\
0.05082 & AOD\_297 \\
0.04256 & AOD\_297.5 \\
0.04915 & AOD\_298 \\
0.05339 & AOD\_298.5 \\
0.0521 & AOD\_299 \\
0.0563 & AOD\_299.5 \\
0.05211 & AOD\_300 \\
0.05446 & AOD\_300.5 \\
0.05641 & AOD\_301 \\
0.05911 & AOD\_301.5 \\
0.05837 & AOD\_302 \\
0.05654 & AOD\_302.5 \\
0.05637 & AOD\_303 \\
0.05911 & AOD\_303.5 \\
0.06221 & AOD\_304 \\
0.0617 & AOD\_304.5 \\
0.06055 & AOD\_305 \\
0.05969 & AOD\_305.5 \\
0.06106 & AOD\_306 \\
0.06151 & AOD\_306.5 \\
0.06109 & AOD\_307 \\
0.06102 & AOD\_307.5 \\
0.06112 & AOD\_308 \\
0.05896 & AOD\_308.5 \\
0.05981 & AOD\_309 \\
0.06092 & AOD\_309.5 \\
0.06128 & AOD\_310 \\
0.06248 & AOD\_310.5 \\
0.06266 & AOD\_311 \\
0.06244 & AOD\_311.5 \\
0.06146 & AOD\_312 \\
0.06306 & AOD\_312.5 \\
0.06236 & AOD\_313 \\
0.06216 & AOD\_313.5 \\
0.06163 & AOD\_314 \\
0.06109 & AOD\_314.5 \\
0.06058 & AOD\_315 \\
0.06143 & AOD\_315.5 \\
0.06154 & AOD\_316 \\
0.06132 & AOD\_316.5 \\
0.06198 & AOD\_317 \\
0.06208 & AOD\_317.5 \\
0.06153 & AOD\_318 \\
0.06167 & AOD\_318.5 \\
0.06209 & AOD\_319 \\
0.06263 & AOD\_319.5 \\
0.06239 & AOD\_320 \\
0.06294 & AOD\_320.5 \\
0.06408 & AOD\_321 \\
0.06103 & AOD\_321.5 \\
0.06081 & AOD\_322 \\
0.06198 & AOD\_322.5 \\
0.06209 & AOD\_323 \\
0.06283 & AOD\_323.5 \\
0.06396 & AOD\_324 \\
0.06505 & AOD\_324.5 \\
0.06508 & AOD\_325 \\
0.06573 & AOD\_325.5 \\
0.06572 & AOD\_326 \\
0.06501 & AOD\_326.5 \\
0.06474 & AOD\_327 \\
0.0639 & AOD\_327.5 \\
0.0644 & AOD\_328 \\
0.06489 & AOD\_328.5 \\
0.06504 & AOD\_329 \\
0.0651 & AOD\_329.5 \\
0.06543 & AOD\_330 \\
0.06558 & AOD\_330.5 \\
0.06525 & AOD\_331 \\
0.06546 & AOD\_331.5 \\
0.06584 & AOD\_332 \\
0.06598 & AOD\_332.5 \\
0.06566 & AOD\_333 \\
0.06592 & AOD\_333.5 \\
0.06643 & AOD\_334 \\
0.06669 & AOD\_334.5 \\
0.06659 & AOD\_335 \\
0.06676 & AOD\_335.5 \\
0.06725 & AOD\_336 \\
0.06766 & AOD\_336.5 \\
0.06754 & AOD\_337 \\
0.06775 & AOD\_337.5 \\
0.06769 & AOD\_338 \\
0.06857 & AOD\_338.5 \\
0.06795 & AOD\_339 \\
0.06759 & AOD\_339.5 \\
0.06771 & AOD\_340 \\
0.06853 & AOD\_340.5 \\
0.06766 & AOD\_341 \\
0.06773 & AOD\_341.5 \\
0.06835 & AOD\_342 \\
0.06879 & AOD\_342.5 \\
0.06639 & AOD\_343 \\
0.06634 & AOD\_343.5 \\
0.06638 & AOD\_344 \\
0.06642 & AOD\_344.5 \\
0.06593 & AOD\_345 \\
0.06787 & AOD\_345.5 \\
0.06794 & AOD\_346 \\
0.06754 & AOD\_346.5 \\
0.06782 & AOD\_347 \\
0.06901 & AOD\_347.5 \\
0.06837 & AOD\_348 \\
0.06846 & AOD\_348.5 \\
0.06928 & AOD\_349 \\
0.06937 & AOD\_349.5 \\
0.06896 & AOD\_350 \\
0.07022 & AOD\_350.5 \\
0.07031 & AOD\_351 \\
0.06975 & AOD\_351.5 \\
0.06989 & AOD\_352 \\
0.07064 & AOD\_352.5 \\
0.07133 & AOD\_353 \\
0.07209 & AOD\_353.5 \\
0.07342 & AOD\_354 \\
0.07431 & AOD\_354.5 \\
0.07486 & AOD\_355 \\
0.07434 & AOD\_355.5 \\
0.07405 & AOD\_356 \\
0.07435 & AOD\_356.5 \\
0.07383 & AOD\_357 \\
0.07229 & AOD\_357.5 \\
0.07375 & AOD\_358 \\
0.07471 & AOD\_358.5 \\
0.07492 & AOD\_359 \\
0.07484 & AOD\_359.5 \\
0.07569 & AOD\_360 \\
0.07545 & AOD\_360.5 \\
0.07436 & AOD\_361 \\
0.07164 & AOD\_361.5 \\
0.07609 & AOD\_362 \\
0.05581 & AOD\_362.5 \\
0.0216 & AOD\_363 \\
\end{longtable}

\begin{verbatim}
range 0.00356534 0.0760932 
\end{verbatim}

@@

\begin{verbatim}

Call:
lm(formula = export$Brewer_AOD340 ~ export$Cimel_AOD340)

Residuals:
      Min        1Q    Median        3Q       Max 
-0.107947 -0.035666  0.002093  0.019482  0.312855

Coefficients:
                    Estimate Std. Error t value Pr(>|t|)    
(Intercept)          0.09636    0.01866   5.163 1.37e-06 ***
export$Cimel_AOD340  0.69840    0.04813  14.511  < 2e-16 ***
---
Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1

Residual standard error: 0.05916 on 93 degrees of freedom
  (195 observations deleted due to missingness)
Multiple R-squared:  0.6936,    Adjusted R-squared:  0.6904 
F-statistic: 210.6 on 1 and 93 DF,  p-value: < 2.2e-16
\end{verbatim}

\begin{verbatim}

Call:
lm(formula = export$Brewer_AOD340 ~ 0 + export$Cimel_AOD340)

Residuals:
     Min       1Q   Median       3Q      Max 
-0.17265 -0.02907  0.00868  0.03643  0.31808

Coefficients:
                    Estimate Std. Error t value Pr(>|t|)    
export$Cimel_AOD340  0.93340    0.01766   52.85   <2e-16 ***
---
Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1

Residual standard error: 0.06675 on 94 degrees of freedom
  (195 observations deleted due to missingness)
Multiple R-squared:  0.9674,    Adjusted R-squared:  0.9671 
F-statistic:  2793 on 1 and 94 DF,  p-value: < 2.2e-16
\end{verbatim}

{\centering \includegraphics[width=1\linewidth]{GHI_enh_read_aod_brewer_files/figure-latex/unnamed-chunk-4-145}

\caption{ - empty caption - }\label{fig:unnamed-chunk-4-145}
\end{figure}
\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_read_aod_brewer_files/figure-latex/unnamed-chunk-4-146}

\caption{ - empty caption - }\label{fig:unnamed-chunk-4-146}
\end{figure}
